### 2021-09-08 input/related_work.tex
revert related work

\noindent Distributing this index among \processes circumvents these
issues~\cite{voronet, ipfs, mdht, squirrel, coin_19}, but still raises
locality issues where \processes
\begin{inparaenum}[(i)]
\item request to a possibly far away location service the content
  location, and then
\item request the actual content from far away replicas.
\end{inparaenum}
For instance, using \underline{d}istributed \underline{h}ash
\underline{t}ables (DHT)~\cite{ipfs, mdht, squirrel}, each \process
stores a part of the index defined by an interval between hash values.
The hash values are the keys to retrieve the associated content
location.  Before downloading any content, a \node asks for its
location using its key. After a series of round-trips between possibly
distant DHT servers, the \node gets a list of available
replicas. Contrarily to \NAME, such services do not ensure to include
the closest replica.

>>>>

\noindent Distributing this index among \processes circumvents these
issues~\cite{voronet, ipfs, mdht, squirrel, triukose2011measuring,
  coin_19}, but still raises locality issues where \processes
\begin{inparaenum}[(i)]
\item request to possibly far away location services the content
  location, and then
\item request the actual content from possibly far away replicas.
\end{inparaenum}
For instance, using \underline{d}istributed \underline{h}ash
\underline{t}ables (DHT)~\cite{ipfs, mdht, squirrel}, each \process
stores a part of the index defined by an interval between hash values.
The hash values are the keys to retrieve the associated content
location.  Before downloading any content, a \node asks for its
location using its key. After a series of round-trips between possibly
distant DHT servers, the \node gets a list of available
replicas. Contrarily to \NAME, such services do not ensure to include
the closest replica.
